### 2015-05-08 ase-2015-tex/intro.tex
Some minor rewrites to the introduction, renamed Semantics subsection.

An alternative approach which does not under-approximate the heap is
Generalized Symbolic Execution
(\gsetxt{})~\cite{Cadar:2008,KiasanKunit,GSE03,Rosner:2015}.  On symbolic
dereferencing operations,~\gsetxt{} partitions the input space between the
various possible aliasing configurations on-the-fly and also creates
non-deterministic choice points on the current path in order to
explore each heap configuration. This approach, however, is
inefficient because it does not treat heap allocated data as symbolic,
but instead concretizes all possible heap configurations.

\bah{The contribution of this work is a method for modeling and solving systems 
of constraints over a symbolic input heap.} The
result of which, unlike~\gsetxt{}, is the ability to efficiently generate
and update \emph{symbolic heaps} to produce a single path constraint
that is sound and complete up to the point of execution. This is
accomplished by representing the symbolic heap with a field sensitive
points-to graph with edges annotated with disjunctive formulas
describing aliasing relationships. Where~\gsetxt{} branches the heap at every
de-reference, the symbolic heap in this work splits only at reference
comparison operations or field operations that may throw exceptions.

>>>>

An alternative approach which does not under-approximate the heap is
Generalized Symbolic Execution
(\gsetxt{})~\cite{Cadar:2008,KiasanKunit,GSE03,Rosner:2015}.  On symbolic
dereferencing operations,~\gsetxt{} partitions the input space between the
various possible aliasing configurations on-the-fly and also creates
non-deterministic choice points on the current path in order to
explore each heap configuration. \bah{This approach, however, is
inefficient because it initiates a new search path for every possible heap configuration.
The resulting path growth is exponential in the number of dereferencing operations.}

The contribution of this work is a method for modeling and solving systems 
of constraints over a symbolic input heap.The
result of which, unlike~\gsetxt{}, is the ability to efficiently generate
and update \emph{symbolic heaps} to produce a single path constraint
that is sound and complete up to the point of execution. This is
accomplished by representing the symbolic heap with a field sensitive
points-to graph with edges annotated with disjunctive formulas
describing aliasing relationships. Where~\gsetxt{} branches the heap at every
de-reference, the symbolic heap in this work splits only at reference
comparison operations or field operations that may throw exceptions.

### 2015-05-08 ase-2015-tex/summary-heap.tex
Some minor rewrites to the introduction, renamed Semantics subsection.

\bah{\figref{fig:exampleHeap} shows an example symbolic heap. References are 
represented by circles and locations are represented by squares. Arrows leaving
references correspond to the value sets returned by the $\cfgnt{L}$ function, and 
arrows leaving the squares correspond to the $\cfgnt{R}$ function.}

@@

\subsection{Semantics}

>>>>

\figref{fig:exampleHeap} shows an example symbolic heap. References are 
represented by circles and locations are represented by squares. Arrows leaving
references correspond to the value sets returned by the $\cfgnt{L}$ function, and 
arrows leaving the squares correspond to the $\cfgnt{R}$ function.

@@

\subsection{Symbolic Execution Semantics}
